\cvsection{Work Experience}

\begin{cventries}
  \cventry
    {Web Developer - Intern} % Job title
    {FULL Creative} % Organization
    {Chennai, IN} % Location
    {June 2021 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developing Email templates and web pages.}
      \end{cvitems}
    }
    
  \cventry
    {Software Engineer Trainee} % Job title
    {HHAeXchange} % Organization
    {Ahmedabad, IN} % Location
    {December 2020 - April 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on Clinical Module of Product.}
        \item {Developed the feature on Improvement of Patient's Monitoring and Tracking.}
        \item {Tech Stack: .NET framework, C\#, Javascript, SSMS}
      \end{cvitems}
    }
  \cventry
    {(Core Team Member | Head of Web Development Team) - PRESENT | Web Development Team Member(till August'20)} % Job title
    {Developer Student Club DDU} % Organization
    {Nadiad, IN} % Location
    {March 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The Developer Student Clubs (DSC) program is a grassroots channel through which we provide development skills for students, towards employability. Spreading awareness about new technologies and guiding students.}
        \item{Conducted workshop on Progressive Web Applications(PWA) and Accelerated Mobile Pages(AMP).}
        \item{Hosted Webinar on GraphQL and its Architecture on June 2020.}
        \item{Worked with Dart's Flutter Framework and GSuite Essentials.}
      \end{cvitems}
    }

    
\end{cventries}
