\cvsection{Projects}

\begin{cventries}
  \cventry
    {Flutter | File-System | Dart } % Empty position
    {File Explorer and Optimizer} % Project
    {} % Empty location
    {December 2019 - March 2020} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Android Application that manages file system and removes duplicate files using MD5 Hash.}
		\item {Users are able to see category-wise files (e.g. audio, documents, video...) using MIME type.}
		\item{Users can search files/folders by name and also dark mode is supported.}
      \end{cvitems}
    }
    \cventry
    {MEAN(MongoDB, Express, Angular 8, Node.js) | jQuery | Passport.js | DataTables} % Empty position
    {E-Tourism} % Project
    {} % Empty location
    {August 2019 - October 2019} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Users can easily search for travel agencies or tour guides.}
      	\item {Fully Responsive Front-end using Angular 8, DataTables and provides smooth UI using jQuery.}
		\item {Backend with MongoDB, Express.js and  Passport.js provides authentication.}
      \end{cvitems}
    }
    \vspace{1.9 mm}
    \cventry
    {ASP.NET | MVC Application | Entity Framework} % Empty position
    {Student Academic Project Management and Performance Analysis} % Project
    {} % Empty location
    {August 2019 - October 2019} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {ASP.NET MVC Application - Academic Project Management and Performance Analysis using Graph(Canvas.js).}
      \end{cvitems}
    }
    \cventry
    {Django | Python | Bootstrap4} % Empty position
    {Quiz Application} % Project
    {} % Empty location
    {January 2019 - March 2019} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Dynamic Application for quiz creation(multi-choice) and play using Python's Django framework.}
		\item {It gives smooth environment to quiz-master to do operation with question-answer, and Player to play quiz.}
      \end{cvitems}
    }
    \cventry
    {PHP | CSS | MySQL} % Empty position
    {Fantasy Cricket League} % Project
    {} % Empty location
    {January 2019 - March 2019} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Dynamic Application for Fantasy cricket contests and Live Play.}
		\item {Backend built using PHP script and frontend designed using HTML,CSS.}
      \end{cvitems}
    }
\end{cventries}